### 2019-05-25 thesis-template/msc-thesis.tex
update

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization). Another reason is it yields a reasonable source-target structure. We introduce a new operator called \textit{propagate}, permitting us to pre-define the propagation in a symbolic manner. The propagation definition denotes the transformation from one grid (A-buffer) into another (B-buffer) through proper application of the \textit{propagate}-operator to each cell. We will fill this operator with meaning in sect. \ref{sec:trans} in form of a precise mathematical formulation respectiively. Each Grid or Buffer is basically a set of cells defined as $\mathcal{C} = \{\mathbf{c}_1, \mathbf{c}_2, ..., \mathbf{c}_n\}$.  The dual buffer result $\mathcal{C'}$ is denoted symbolically as follows for all cells with a mean intensity greater than zero (which do not contain trivial Null samples):
\begin{align}
	\mathcal{C'} = \mathop{propagate}\{c_i\in \mathcal{C} \ \mid \ |\mean{I}_i| > 0\} \hskip 5pt {\forall } \ i \in [1,\mathop{dim}]
\end{align}
Note that, $\mathop{dim}=width\cdot height$, which equals the tensor field resolution in this case.

@@

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda>0$ and the other $\lambda=0$) incorporated. For this we setp up bidirectional delta-pulses as glyphs to have the whole energz transmitted in just one, discrete direction .
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.5\textwidth]
    {img/total_anisotropy.png}
  }
  \caption{Total Anisotropy Test}
  \label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as we use 8 discrete directions to propagate whereas the circle uses much more. Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter/escape each) as observable in Fig. \ref{anisotropy}.
\section{Energy Conservation Test}
The Energy Conservation Test was done in similar manner as the Propagation Attenuation Test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for about 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum in iteration 0 in absolute values. This approach yields the following graph:
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.5\textwidth]
    {img/sum_difference.png}
  }
  \caption{Sum Error}
  \label{anisotropy}
\end{figure}

>>>>

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization). Another reason is it yields a reasonable source-target structure. We introduce a new operator called \textit{propagate}, permitting us to pre-define the propagation in a symbolic manner. The propagation definition denotes the transformation from one grid (A-buffer) into another (B-buffer) through proper application of the \textit{propagate}-operator to each cell. We will fill this operator with meaning in sect. \ref{sec:trans} in form of a precise mathematical formulation respectively. Each Grid or Buffer is basically a set of cells defined as $\mathcal{C} = \{\mathbf{c}_1, \mathbf{c}_2, ..., \mathbf{c}_n\}$.  The dual buffer result $\mathcal{C'}$ is denoted symbolically as follows for all cells with a mean intensity greater than zero (which do not contain trivial Null samples):
\begin{align}
	\mathcal{C'} = \mathop{propagate}\{c_i\in \mathcal{C} \ \mid \ |\mean{I}_i| > 0\} \hskip 5pt {\forall } \ i \in [1,\mathop{dim}]
\end{align}
Note that, $\mathop{dim}=width\cdot height$, which equals the tensor field resolution in this case.

@@

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda>0$ and the other $\lambda=0$) incorporated. For this we setp up bidirectional delta-pulses as glyphs to have the whole energz transmitted in just one, discrete direction .
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.5\textwidth]
    {img/total_anisotropy.png}
  }
  \caption{Total Anisotropy Test}
  \label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as we use 8 discrete directions to propagate whereas the circle uses much more. Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter/escape each) as observable in Fig. \ref{anisotropy}.
\section{Energy Conservation Test}
The Energy Conservation Test was done in similar manner as the Propagation Attenuation Test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for about 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum in iteration 0 in absolute values. This approach yields the following graph:
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.7\textwidth]
    {img/sum_difference.png}
  }
  \caption{Sum Error: src intensities: red: 1.0, blue 2.0, green: 5,0}
  \label{anisotropy}
\end{figure}

The approach remains stable until iteration 40, which is at the time (point) when the numbers are to small and get rounded down under the double machine epsilon. You can see heavy fluctuations because the numbers get rounded upwards likewise. But what is lost, is lost and can not be gained back. The error is accumulating gradually and with faster slope for higher source intensities, since floting point precision, i.e. rounding errors operate more heavily on large numbers leading to a greater absolute $\Delta E$
